\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}

\title{SE 3XA3: Development Plan\\Staroids}

\author{Team 20, Staroids
		\\ Moziah San Vicente, 400091284, sanvicem
		\\ Eoin Lynagh, 400067675, lynaghe
		\\ Jason Nagy, 400055130, nagyj2
}

\date{Friday September 28, 2018}

\input{../Comments}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Sept 21 & Eoin, Jason, Moziah & Added questions to be answered\\
Sept 23 & Jason & Added Communication Plan content\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

Put your introductory blurb here.

\section{Team Meeting Plan}
Eoin
When?Where?Frequency?Roles?Rules for agendas?Upcoming milestones?Discuss problems?

Meetings Monday 5:30 (After 3BB4)

Agendas:
Form - Meeting Minutes
*Meeting Minutes obey Harvard guidelines
Chair - Jason/ Wallace
Scribe - Eoin

\section{Team Communication Plan}
Jason

Most work related jobs and tasks will be discussed through Facebook Messenger. The aformentioned discussion includes assigning work, talking about current issues, discussing what is next and how implementations should be done. Facebook Messenger will be used in addition to the scheduled meetings. The meetings will be about larger issues while Facebook Messenger will have simpler issues. If someone is unable to use Facebook Messenger for whatever reason, email can also be used for casual work discussion. Some examples of issues that are Facebook Messenger worthy are bugs in the program, code portions where the coder is unsure how to solve a problem, letting the team know what someone is currently working on.\\
For more time critical issues, the phone is to be used. It can be through text or call, but call is preferred because it allows for synchronous communication. Some example issues worth of phone communication include questions for work that are due soon and application crashing bugs, should they occur.\\
The members of Staroids have all exchanged phone and Facebook information.\\

\section{Team Member Roles}
Jason

The leader of Staroids will be Jason. As leader, he is responsible for organizing meetings.\\
The scribe of Staroids will be Eoin. Eoin is in charge of meeting agendas and ensuring meeting documents are current and accurate. He is also responsible for assembling the meeting agendas from information from everyone.\\
The technology expert and submitter will be Moziah. Moziah is responsible for researching and implementing new technologies and tools to be used in the project while also ensuring that the Git repo is maintained properly. Moziah will also ensure the final versions of files are properly tagged.\\
As a group, Staroid members will

\section{Git Workflow Plan}
Jason
branching - personal branches
milestones - deliverables and decided upon goals
labels - to be researched
atom tele-type - same file editing in real time with others

\section{Proof of Concept Demonstration Plan}
All
research - look to slides

\section{Technology}
Moe
JavaScript - Canvas
HTML5
Case based?
LaTeX (pdflatex)

\section{Coding Style}
Eoin
\subsection{File Names}
File names will be written using camel case, and will use a descriptive title. For example, the title of this document is styleGuidelines. 
\subsection{Variable Names}
Variable names will be written using camel case, and will be written as follows baseAttributeDescriptor, so for example, a variable representing the velocity of a ball would be named velocityBall.
\subsection{Javascript}
Javascript code will be written to follow the \href{https://google.github.io/styleguide/jsguide.html}{Google Javascript Style Guide}, which details coding standards for source code in JavaScript. However, the style of Variable/File names is described above, and may not follow the Google Style guide.
file names - camel case
variable names - camel case, [base attribute][descriptor]
follow https://google.github.io/styleguide/jsguide.html

\section{Project Schedule}
Moe
Provide a pointer to your Gantt Chart.

\section{Project Review}

- not actually completed

\end{document}
